% !TEX program = xelatex

\documentclass{resume}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Yuanyuan(Walker) Xia}

\basicInfo{
  \email{xiayuan1992@gmail.com} \textperiodcentered\
  \phone{(+86) 188-4260-4162}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Dalian University of Technology (DUT)}, Dalian, China}{SEP. 2015 -- JUN. 2018}
\textit{M.S.} in Information System
\datedsubsection{\textbf{Dalian Polytechnic University (DPU)}, Dalian, China}{SEP. 2011 -- JUL. 2015}
\textit{B.S.} in Information Management \& Information System

\section{\faUsers\ Experience }
\datedsubsection{\textbf{Envision Energy} Shanghai, China}{NOV. 2017 -- Present}
\role{Senior Software Engineer}{}
Brief introduction: Responsible for building rule engine service and data subscription service for IoT platform and managing the middleware service(Kafka \& Zookeeper)
\begin{itemize}
  \item Delicate system design for rule engine to make it reach a high stability and throughput
  \item Build a subscription service from bottom to up
  \item Manage the base service of Kafka \& Zookeeper, include user guidance and troubleshooting
\end{itemize}

\datedsubsection{\textbf{Rule Engine Projects}}{JUL. 2018 -- Present}
\role{IoT, SQL-like Parser \& Executor, TSDB, Redis, Kafka, High Throughput}{}
IoT Base Service
\begin{itemize}
  \item Participate and be responsible for the development and iteration of the rule engine of the IoT platform
  \item Design and implement SQL-like interpreter, Users can forward the required device data to the destination by writing SQL-like expressions, Such as TSDB, Redis, Kafka Topic, Streaming Input, etc.
  \item Processing tens of billions of device points data per day, with an average daily data throughput of tens of TBs
\end{itemize}

\datedsubsection{\textbf{Data Subscription Projects}}{OCT. 2018 -- Present}
\role{Data Subscription, Netty, Websocket, Protobuf, Kafka}{}
Data transmission
\begin{itemize}
    \item Responsible for and participate in the subscription service of IoT platform data
    \item The project consists of subscription Meta service, subscription Server and Client, Users can describe subscription requirements through the Meta service, Use the Client SDK (Java/Python/C\#) provided by the application to initiate a subscription to the Server.
    \item Ensure complete and reliable subscription data, C/S communication uses a custom binary protocol built on Protobuf, Network IO is built on Netty, Support websocket protocol.
    \item Single instance (2C4G) Server data processing capability at 2w Messages/sec, C/S throughput at 5w Messages/sec.
\end{itemize}

\datedsubsection{\textbf{Middleware Service}}{JUN. 2019 -- Present}
\role{Kafka, Kafka Client SDK, Zookeeper, Microservices}{}
Middleware
\begin{itemize}
    \item Responsible for the platform's message queue service, Have a detailed reading and understanding of the specific implementation of Kafka and RocketMQ
    \item Encapsulate the native client of Kafka and RocketMQ to facilitate quick access to the MQ service inside the platform
    \item Build monitoring metric for MQ and Zookeeper
    \item Package Dubbo service to adapt to the environment inside the platform, track the progress of the community microservices framework, responsible for daily use problem solving
\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Java, Python, C/C++
  \item Big Data: Apache Kafka, Apache Zookeeper
  \item Platform: Linux
  \item Development: Web,Desktop
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{\nth{3} Prize}, Award on Dalian University of Technology Mathematical Contest }{SEP. 2016}
\datedline{\textit{Top Performance}, Top 25\% of academic performance of graduate student }{JUN. 2018}
\datedline{\textit{Top Performance}, Excellent staff }{MAY. 2019}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: https://wuyi.me
  \item GitHub: https://github.com/dut-xiayuan
  \item Languages: English - Fluent, Mandarin - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
